Reviewer Comments (Scientific Reports)

### 2020-01-08 notebook/sci_rep_reviews.Rmd
Start a new set of responses

>>>>

I have taken the following actions:

1. Re-run simulations while calculating the correlation between off-diagonal elements of A[i,j] and A[j,i] to see if the correlation changes with $\gamma$ across $S$. It does not. I also generated systems of known correlation coefficients to assess how this modulated $\gamma$'s affect on stability. It did not.

2. Run simulations across multiple structured network types to confirm the robustness of results. Network types include (a) cascade food webs, (b) small world networks, and (c) scale-free network.
